Supplementary Material\\ \textit{Cross Validation Approaches for Penalized Cox Regression}

### 2019-05-22 main.tex
Edits to 3.3

\begin{figure}[ht]
  \centering
  \includegraphics[height= 7cm ]{./manuscript_figure/figure_2_new.png}
  \caption{\label{Fig:mse-brier-c} Simulation comparing 4 CV methods. The horizontal axis in all three plots is $s$, which represents the signal strength in the data. The value of $s$ is varied from 0.4 to 0.9.  $\log(\text{MSE ratio})$, relative to the oracle modle is plotted in the left panel. Out-of-sample Brier scores are plotted in the middle. Out-of-sample C index is plotted in the right panel. For each simulated data set, n = 120, p = 1000. Expected censoring percentage is 10$\%$. }
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[height= 8cm ]{./manuscript_figure/figure_4.png}
  \caption{\label{Fig:loocv}Simulation comparing LOO and 10-fold CV across three different approaches. With $N = 200$ replications, the data sets generated have dimension $n = 120$ and $p = 1000$. The horizontal axis is the signal strength. The verticle axis is the $\log$(MSE ratio). In each panel, the LOO version and 10-fold version of the same approach are plotted. The 10-fold standard approach is plotted as the blue line in all three panels as a baseline for comparison. }
\end{figure}

@@

On the other hand, the LOOCV version of the linear predictor approach surpasses the standard 10-fold CV by having smaller $\log(\text{MSE ratio})$ across all signal strength levels. At the same time, even the 10-fold version of the linear predictor approach also outperforms the leave-one-out version of the V$\&$VH approach and the deviance residual approach. Even though the leave-one-out cross validation improves the predictive accuracy for V$\&$VH and deviance residual approach, the magnitude of improvement in predictive performance is smaller than switching to the linear predictor approach.

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[height= 7cm ]{./manuscript_figure/figure_2_new.png}
  \caption{\label{Fig:mse-brier-c} Simulation comparing 4 CV methods. The horizontal axis in all three plots is $s$, which represents the signal strength in the data. The value of $s$ is varied from 0.4 to 0.9.  $\log(\text{MSE ratio})$, relative to the oracle modle is plotted in the left panel. Out-of-sample Brier scores are plotted in the middle. Out-of-sample C index is plotted in the right panel. For each simulated data set, n = 120, p = 1000. Expected censoring percentage is 10$\%$. \note{For the sake of consistency, Signal should be capitalized in the x-axis label above.}}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[height= 8cm ]{./manuscript_figure/figure_4.png}
  \caption{\label{Fig:loocv}Simulation comparing LOO and 10-fold CV across three different approaches. With $N = 200$ replications, the data sets generated have dimension $n = 120$ and $p = 1000$. The vertical axis is the $\log$(MSE ratio). In each panel, the LOO version and 10-fold version of the same approach are plotted. In all three panels, 10-fold standard cross-validation is included as a baseline for comparison (blue line). \note{Again, Signal should be capitalized.}}
\end{figure}

@@

On the other hand, the LOOCV version of the linear predictor approach surpasses standard 10-fold CV, with a smaller $\log(\text{MSE ratio})$ across all signal strength levels. At the same time, even the 10-fold version of the linear predictor approach outperforms the leave-one-out version of the V$\&$VH approach and the deviance residual approach. In other words, although adopting a leave-one-out approach improves the predictive accuracy for V$\&$VH and deviance residual cross-validation, the magnitude of improvement in predictive performance is smaller than the improvement gained from switching to the linear predictor approach.
